\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\input{preamble}
\input{article/auto_names}

\usepackage{orcidlink}

\defineauthors[false]{gilles,bert,daan,jarne,gustav}
    
\begin{document}

\title{\dataset: A Synchronized Multimodal RF-Acoustic Dataset for Positioning in Distributed Environments%
\thanks{Identify applicable funding agency here. If none, delete this.}%
\thanks{For the purpose of open access, the author has applied a CC BY public copyright license to any Author Accepted Manuscript version arising from this submission.}}

\author{
%%%% AUTHORS %%%%
\IEEEauthorblockN{%
Gilles Callebaut\,\orcidlink{0000-0003-2413-986X}\IEEEauthorrefmark{1},
Daan Delabie\,\orcidlink{0000-0003-2413-986X}\IEEEauthorrefmark{1},
Bert Pyck\,\orcidlink{0000-0003-2413-986X}\IEEEauthorrefmark{1},
Jarne Van Mulders\,\orcidlink{0000-0003-2413-986X}\IEEEauthorrefmark{1},
Gustav Nilsson\,\orcidlink{0000-0003-2413-986X}\IEEEauthorrefmark{2}
}
%%%% AFFILIATIONS %%%%% ...
\IEEEauthorblockA{\IEEEauthorrefmark{1}% 2nd affiliations
Department of Electrical Engineering, KU Leuven, Belgium}
\IEEEauthorrefmark{2}% 2nd affiliations
Lund}

\maketitle


\gilles{first cleaning up the GenAI crap.}

\begin{abstract}
This paper documents \dataset{}, a synchronized measurement campaign for distributed wireless sensing and positioning in the Techtile testbed. It consists of \gls{rf} and acoustic measurements distributed over an 3-by-6m area indoor, yeidlign in total \num{2872} spatial samples. an antenna and omnidirectional speaker is co-located. The channel-state-information is estimated across a 42 antennas over a ceiling spanning 4x8m. The acoutsic modality is synchronized microphone waveforms XX microphones containing the received aplitude.

RF 920 mhz. Acoustic ....

phase-coherent

 Beyond documenting the recorded assets, we also report the now-implemented downstream experiments: a walk-based acoustic positioning pipeline that performs anchor selection, pulse-compression ranging, and least-squares localization on held-out rover trajectories, together with exploratory phase-based \gls{rf} positioning utilities. We detail how the measurements are recorded, quantify per-experiment coverage, describe the RF and acoustic data contents, and explain how the aligned modalities support RF-only, acoustic-only, and joint positioning workflows.
\end{abstract}

\begin{IEEEkeywords}
dataset, positioning, localization, Techtile, channel state information, multimodal sensing
\end{IEEEkeywords}

\tableofcontents % jst to keep an overview

\input{sections/introduction}
\input{sections/platform}
\input{sections/campaign}
\input{sections/capabilities}
\input{sections/discussion}
\input{sections/conclusion}

\section*{Acknowledgment}
Bert Cox, Geoffrey Ottoy.



\printbibliography%

\end{document}
