\section{Experimental Campaign and Coverage}
\label{sec:campaign}

The \dataset{} campaign contains 12 named experiments (\texttt{EXP001}--\texttt{EXP012}) with rover position logs stored in \texttt{server/record/data/}. Across those runs, the recorded rover coordinates span approximately 0.81~m to 6.87~m in the Qualisys $x$-axis and 0.71~m to 3.60~m in the $y$-axis. The experiments are not all mapped to the same spatial subregion, which is evident from the per-experiment coordinate ranges in \cref{tab:experiments}. This is useful for capability analysis because it shows that the campaign is composed of several sub-surveys rather than one monolithic raster over a single contiguous rectangular patch.

The most rigorous release-level coverage statement is provided by the shipped completeness report, \texttt{measurement\_completeness\_report.md}. That report audits the union of rover logs, the merged \gls{rf} dataset, and the available acoustic NetCDF files. It identifies 7{,}579 unique \texttt{(experiment\_id, cycle\_id)} pairs observed in at least one modality. Of these, 5{,}011 have populated \gls{rf} data, 3{,}714 have acoustic data, and 2{,}872 are complete triplets with \gls{rf}, rover position, and acoustic data. Put differently, the presently complete tri-modal subset corresponds to 37.9\% of the logged rover stops, 57.3\% of the populated \gls{rf} cycles, and 77.3\% of the available acoustic cycles.

\begin{table*}[t]
    \centering
    \caption{Per-experiment campaign summary derived from the rover position logs and the shipped completeness report. Coordinate ranges are in meters.}
    \label{tab:experiments}
    \scriptsize
    \setlength{\tabcolsep}{5pt}
    \begin{tabular}{lcccccc}
        \toprule
        Experiment & $x$ range & $y$ range & Rover cycles & \gls{rf} cycles & Acoustic cycles & Complete tri-modal cycles \\
        \midrule
        EXP001 & [1.15, 1.75] & [2.55, 3.16] & 791  & 0    & 0    & 0 \\
        EXP002 & [0.81, 2.05] & [2.26, 3.50] & 914  & 0    & 0    & 0 \\
        EXP003 & [1.31, 2.54] & [2.25, 3.48] & 529  & 529  & 529  & 529 \\
        EXP004 & [1.92, 2.54] & [2.25, 3.48] & 19   & 0    & 0    & 0 \\
        EXP005 & [1.58, 2.83] & [0.71, 3.47] & 1618 & 777  & 1618 & 777 \\
        EXP006 & [2.19, 3.44] & [1.39, 2.63] & 238  & 238  & 238  & 238 \\
        EXP007 & [3.01, 4.27] & [1.42, 2.68] & 379  & 378  & 379  & 378 \\
        EXP008 & [3.59, 4.84] & [0.89, 2.13] & 201  & 201  & 201  & 201 \\
        EXP009 & [3.07, 4.32] & [1.90, 3.15] & 1356 & 1355 & 0    & 0 \\
        EXP010 & [4.48, 5.73] & [1.31, 2.55] & 458  & 458  & 458  & 458 \\
        EXP011 & [5.63, 6.87] & [1.07, 2.31] & 291  & 291  & 291  & 291 \\
        EXP012 & [4.38, 5.64] & [2.34, 3.60] & 785  & 784  & 0    & 0 \\
        \bottomrule
    \end{tabular}
\end{table*}

Several observations follow directly from \cref{tab:experiments}. First, the campaign is not uniformly complete. EXP003, EXP006, EXP008, EXP010, and EXP011 are fully aligned. EXP007 is nearly complete, missing only one \gls{rf} cycle. EXP005 is the largest dense tri-modal run in terms of acoustic and rover coverage, but only 777 of its 1{,}618 rover cycles currently have matching \gls{rf} data in the merged dataset. EXP009 is the opposite case: it contributes a large \gls{rf} set without acoustic counterparts in the released completeness state. Finally, EXP001, EXP002, and EXP004 provide rover coverage but not processed \gls{rf} or acoustic cycles in the present release.

The campaign should therefore be interpreted as a layered asset rather than a single homogeneous benchmark. If the research question is purely \gls{rf}-spatial, the usable set is materially larger than if joint \gls{rf}+acoustic analysis is required. \dataset{} is strong precisely because it makes that distinction measurable instead of implicit.
