\section{Introduction}
\glsresetall

Large-scale experimental datasets have become increasingly important for wireless communication, sensing, and positioning research because they decouple algorithm development from scarce hardware testbed time and expose downstream users to realistic synchronization errors, coverage gaps, and multimodal alignment constraints. Recent multimodal releases such as DeepSense~6G show how carefully documented measurement assets can accelerate communication-aware sensing research well beyond their original experimental purpose~\cite{deepSense6g}. In parallel, Techtile was designed exactly as the kind of room-scale, distributed, synchronized infrastructure needed to create such assets for beyond-5G and 6G experimentation~\cite{techtilePrimer,techtileOpen6g}.

\dataset{} packages one concrete synchronized measurement campaign on top of Techtile. It includes the acquisition stack, rover control, acoustic tooling, \gls{rf} measurement scripts, parsing code, completeness checks, processed data products, and notebook-based analysis workflow used during the campaign. This makes the release more than a collection of files: it is the operational record of how synchronized rover, acoustic, and \gls{rf} measurements were acquired and transformed into analysis-ready products.

This paper is intentionally not framed as a benchmark paper for a specific estimator, classifier, or neural architecture. Its purpose is narrower and more practical: to document the experiments that were actually run, quantify what is currently complete in the released data products, and explain what \dataset{} already enables a researcher to do. In that sense, the paper serves as a rigorous companion to the data release. It reconstructs the measurement workflow, summarizes the campaign experiment by experiment, clarifies how the NetCDF products should be interpreted, and distinguishes between the total logged campaign and the presently usable tri-modal subset.

Three aspects of \dataset{} are especially worth documenting. First, the acquisition is genuinely synchronized at the level of the physical rover stop: one orchestrator cycle corresponds to one commanded rover position, one Qualisys sample, one acoustic capture, and one \gls{rf} cycle. Second, the processed products are already structured for downstream use, with explicit availability masks and notebook-backed analysis examples. Third, completeness is uneven across experiments, which makes it essential to state clearly what parts of the campaign support \gls{rf}-only analysis and what parts support fully aligned \gls{rf}+acoustic+position analysis.

The remainder of the paper is as follows. \Cref{sec:platform} describes the platform and acquisition workflow. \Cref{sec:campaign} quantifies the campaign and its present coverage. \Cref{sec:capabilities} discusses the recorded data products and the positioning capabilities already exposed in the analysis workflow. \Cref{sec:discussion} concludes with the main interpretation caveats and current limitations.
